---
title: "Supplemental Code for Toxicon Correspondence (iVAMP)"
author: "Ul-Hasan et al"
output: word_document
---

Contributors to literature review (by order): SU, ERR, VH, TJC, CNK, SAT, SAM  
Contributors to code: SU 

Methods:
Web of Science search of all 71,738,518 peer-reviewed publications
TITLE: (venom* AND microb*) OR TITLE: (venom* AND bacteria*) OR TITLE: (venom* AND fungi*) OR TITLE: (venom* AND virus*)
Timespan=All years. Indexes=SCI-EXPANDED, SSCI, A&HCI, CPCI-S, CPCI-SSH, BKCI-S, BKCI-SSH, ESCI, CCR-EXPANDED, IC.

Results                       129 hits
  Abstract removed            2 (127 included in analysis)
Sum of the Times Cited        1833
Average Citations per Item    14.21
h-index                       23

Microbe, Topic, and Animal columns were added manually

Upload Web of Science search output, clean-up, Figure 1a-c
```{r}

# Upload data
# setwd("~/Desktop/MS_iVAMP-Correspondence/ToxiconX_Correspondence-Final") # update to Github repo when final (after reviews)
Raw = read.csv("Supp_Tab1_Web-of-Science_Raw-Feb10-2019.csv")

# install.packages("wordcloud")
library(wordcloud)
# packageVersion("wordcloud") # v2.6

# Figure 1a: Microbe categories
Microbe = wordcloud(Raw$Microbe) 
Microbe # None category are studies with term 'microb*' that refer to wasp microbracon
dev.copy(png, "Figure1a_Microbe_127-articles.png")
dev.off() 

# Remove all articles for "none" category
Microbe_only = subset(Raw, !(Raw$Microbe=="none")) # 17 articles removed (110 remain)
# Figure 1b: Article topic
Topic = wordcloud(Microbe_only$Topic) 
Topic # 77 antimicrobial, 11 symbiosis
dev.copy(png, "Figure1b_Topic_110-articles.png")
dev.off() 

(77/110)*100 # 70 % antimicrobial
(11/110)*100 # 10 % symbiosis

# Figure 1c: Animal of origin
Animal = wordcloud(Microbe_only$Animal) 
Animal # 77 antimicrobial, 11 symbiosis
dev.copy(png, "Figure1c_Animal_110-articles.png")
dev.off() 

(58/110)*100 # 53 % from snakes, 47% from intevertebrates

```

Superfluous Analyses
```{r}

# install.packages("tidyverse")
library(tidyverse)
# packageVersion("tidyverse") # v1.2.1

# install.packages("tidytext")
library(tidytext)
# packageVersion("tidytext") # v0.2.0

# install.packages("tm")
library(tm)
# packageVersion("tm") # v0.7.6

# install.packages("slam")
library(slam)
# packageVersion("slam") # v0.1.44

# Make the following columns all lower case
Raw$Title = tolower(Raw$Title) 
Raw$Authors = tolower(Raw$Authors)
Raw$Book_Editors = tolower(Raw$Book_Editors)
Raw$Source_Title = tolower(Raw$Source_Title)
# Remove punctuation from these 
Title = Raw$Title %>%
  str_replace_all('[^a-z0-9]+', ' ')
Title = data.frame(Title)
Authors = Raw$Authors %>%
  str_replace_all('[^a-z0-9]+', ' ')
Authors = data.frame(Authors)
Book_Editors = Raw$Book_Editors %>%
  str_replace_all('[^a-z0-9]+', ' ')
Book_Editors = data.frame(Book_Editors)
Source_Title = Raw$Source_Title %>%
  str_replace_all('[^a-z0-9]+', ' ')
Source_Title = data.frame(Source_Title)

NoPunc = cbind(Title, Authors, Book_Editors, Source_Title)
NoPunc$Article = Raw$Article
NoPunc_Annot = merge(NoPunc, Raw, by = "Article")
NoPunc_Annot = NoPunc_Annot[,-c(6:9)] # drops columns with punctuation

# Convert all months to string value
NoPunc_Annot_New = NoPunc_Annot %>% mutate(Publication_Month=
ifelse(Publication_Month == 1 , "JAN",
ifelse(Publication_Month == "JAN" , "JAN",
ifelse(Publication_Month == 2 , "FEB",  
ifelse(Publication_Month == "FEB" , "FEB",
ifelse(Publication_Month == 3 , "MAR",
ifelse(Publication_Month == "MAR" , "MAR",
ifelse(Publication_Month == 4 , "APR",
ifelse(Publication_Month == "APR" , "APR",
ifelse(Publication_Month == 5 , "MAY",
ifelse(Publication_Month == "MAY" , "MAY",
ifelse(Publication_Month == 6 , "JUN",
ifelse(Publication_Month == "JUN" , "JUN",
ifelse(Publication_Month == 7 , "JUL",
ifelse(Publication_Month == "JUL" , "JUL",
ifelse(Publication_Month == 8 , "AUG",
ifelse(Publication_Month == "AUG" , "AUG",
ifelse(Publication_Month == 9 , "SEP",
ifelse(Publication_Month == "SEP" , "SEP",
ifelse(Publication_Month == 10 , "OCT",
ifelse(Publication_Month == "OCT" , "OCT",
ifelse(Publication_Month == 11 , "NOV",
ifelse(Publication_Month == "NOV" , "NOV",
ifelse(Publication_Month == 12 , "DEC",
ifelse(Publication_Month == "DEC" , "DEC",
              "")))))))))))))))))))))))))

```
   